We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-01 paper/paper.tex
+1 paragraph

>>>>

Figure \ref{fig:scatter_ba_ratio} shows the results for the minor to
major axis ratio. 
Corresponding in the ELVIS data are in the appendix in Figure
\ref{fig:scatter_elvis}.
In all cases of comparison (against randomized distribution,
comparasion against simulations and degree of deviation from
sphericity) the results for both the MW and M31 do not seem atypical
or deviated from the expectations for an spherical dsitribution.
